# Results

```{r}
#| label: setup
#| include: false
library(tidyverse)  
library(readxl)
library(sf)
library(scales)
library(ggridges)
library(ggalluvial)
library(lubridate)
library(RColorBrewer)
```

## 1. How Moviegoing in the U.S. Has Shifted Since the Pandemic

### Chart 1. U.S. Theatrical Box Office Revenue by Year

```{r}
## Chart 1: Box office revenue
ggplot(box_office, aes(x = Year, y = Domestic_BoxOffice)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  scale_y_continuous(
    limits = c(0, 12e9),
    breaks = seq(0, 12e9, by = 2e9),
    labels = label_dollar(scale = 1e-9, suffix = "B", accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = 2015:2024,
    minor_breaks = NULL,
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title    = "U.S. Theatrical Box Office Revenue by Year",
    subtitle = "Pre-COVID peak, COVID collapse, and incomplete recovery",
    x = "Year",
    y = "Domestic Box Office (USD, billions)"
  ) +
  theme_minimal(base_size = 16) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background  = element_rect(fill = "white", color = NA),
    panel.grid.minor = element_blank()
  )
```

In 2020, box office revenue plunged from about 11B to just over 2B. Although it has climbed back to around \$8B, it did not return to its old peak and instead settled into a lower range than before the pandemic, which imply that movie industry may now be structurally smaller compared to pre-pandemic.

### Chart 2. Number of Theatrical Releases per Year

```{r}
## Chart 2: Number of releases
ggplot(box_office, aes(Year, Releases)) +
  geom_col(fill = "#4C72B0") +
  scale_x_continuous(
    breaks = 2015:2024,
    minor_breaks = NULL,
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    title    = "Number of Theatrical Releases per Year",
    subtitle = "Industry output remains lower than pre-COVID",
    x = "Year",
    y = "Number of Releases"
  ) +
  theme_minimal(base_size = 16) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background  = element_rect(fill = "white", color = NA),
    panel.grid.minor = element_blank()
  )

```

Similar to Chart 1, the number of theatrical releases dropped sharply in 2020 and remained below pre-pandemic levels. This indicates that studios have reduced their annual output, releasing fewer films than before—likely reflecting shifts in production and distribution strategies.

### Chart 3. Change in AMC Theatres by State (2019–2024)

Based on Chart 1 and Chart 2, box office revenue and the number of releases are both lower than before the pandemic. To understand why, it helps to look at the number of theatres.

```{r}
## 1. Read AMC tables -------------------------------------------------------

amc_2019 <- read_excel(
  "data/AMC_theatres_screens_by_market_2019.xlsx",
  sheet = 1
) |>
  rename(
    state    = `U.S. Markets`,
    theatres = Theatres,
    screens  = Screens
  ) |>
  mutate(state = str_trim(state))

amc_2024 <- read_excel(
  "data/AMC_theatres_screens_by_market_2024.xlsx",
  sheet = 1
) |>
  rename(
    state    = `U.S. Markets`,
    theatres = Theatres,
    screens  = Screens
  ) |>
  mutate(state = str_trim(state))

## 2. Read shapefile + keep only contiguous U.S. ---------------------------

states_sf <- st_read("data/cb_2018_us_state_20m/cb_2018_us_state_20m.shp")

states_sf_conus <- states_sf |>
  filter(!STUSPS %in% c("AK", "HI", "PR", "GU", "VI", "AS", "MP")) |>
  mutate(state = NAME)

# vector of valid state names (lower 48 + DC)
valid_states <- states_sf_conus$state

## 3. Filter AMC tables to states in shapefile -----------------------------

amc_2019_clean <- amc_2019 |>
  filter(state %in% valid_states)

amc_2024_clean <- amc_2024 |>
  filter(state %in% valid_states)

## 4. Compute changes ------------------------------------------------------

state_changes <- amc_2019_clean |>
  select(
    state,
    theatres_2019 = theatres,
    screens_2019  = screens
  ) |>
  inner_join(
    amc_2024_clean |>
      select(
        state,
        theatres_2024 = theatres,
        screens_2024  = screens
      ),
    by = "state"
  ) |>
  mutate(
    theatres_change     = theatres_2024 - theatres_2019,
    theatres_pct_change = (theatres_2024 - theatres_2019) / theatres_2019,
    screens_change      = screens_2024 - screens_2019,
    screens_pct_change  = (screens_2024 - screens_2019) / screens_2019
  )

# Which states from the shapefile are missing change data?
missing_states <- states_sf_conus |>
  st_drop_geometry() |>
  anti_join(state_changes, by = "state") |>
  select(STUSPS, state)

missing_states

## 5. Join back to shapefile for mapping -----------------------------------

map_data <- states_sf_conus |>
  left_join(state_changes, by = "state")
```

```{r}
# Symmetric limits around zero for the diverging scale
lim <- max(abs(map_data$theatres_pct_change), na.rm = TRUE)

ggplot(map_data) +
  geom_sf(
    aes(fill = theatres_pct_change),
    colour = "white",
    linewidth = 0.2
  ) +
  # zoom to lower 48 + DC
  coord_sf(
    xlim   = c(-125, -66),
    ylim   = c(24, 50),
    expand = FALSE
  ) +
  scale_fill_gradient2(
    name     = "Percent change\nin theatres",
    labels   = percent_format(accuracy = 1),
    limits   = c(-lim, lim),
    low      = "#b2182b",   # closures / big declines
    mid      = "white",
    high     = "#2166ac",   # growth
    midpoint = 0,
    na.value = "grey50"
  ) +
  labs(
    title    = "Change in AMC Theatres by State (2019–2024)",
    subtitle = "Percent change in number of AMC theatres\n(Grey = no data / no theatres)",
    caption  = "Source: AMC U.S. Markets Theatres & Screens tables, 2019 vs 2024"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid       = element_blank(),
    axis.title       = element_blank(),
    plot.title.position = "plot"
  )
state_changes |>
  arrange(theatres_pct_change) |>
  select(state, theatres_pct_change) |>
  head(5)   # largest declines

state_changes |>
  arrange(desc(theatres_pct_change)) |>
  select(state, theatres_pct_change) |>
  head(5)   # largest increases
```

Across most of the country, AMC has closed more theatres than it opened between 2019 and 2024 (red states on the map). The biggest cuts are in Nebraska, North Dakota, Kentucky, South Carolina, and South Dakota, where AMC lost two-thirds or more of its theatres. Only a few states show growth, such as Connecticut, Massachusetts, Maryland, California, and New York, and many grey states have no available data at all in either year. Together, this means that AMC's business scope is shrinking a lot.

## 2. While most U.S. sectors recovered strongly post-COVID, the movie industry lags behind

After Section 1 shows that moviegoing is deeply impacted by COVID, Section 2 zooms out to compare movie and media stocks with major sector ETFs to see whether this weaker recovery is unique to movies or part of a broader market pattern.

### Chart 4. Movie Industry vs Major Sector ETFs (Rebased to 1)

```{r}
### --- Load & clean Media data ---
media <- read_csv("data/movie_media_clean.csv", show_col_types = FALSE) |>
  mutate(Date = as.Date(Date))

# --- Load & clean Sector ETFs ---
sectors <- read_csv("data/sector_etfs_clean.csv", show_col_types = FALSE) |>
  mutate(Date = as.Date(Date))


# Rebase each media company to 1
media_rebased <- media |>
  group_by(Ticker) |>
  arrange(Date, .by_group = TRUE) |>
  mutate(base = first(Adj_Close),
         rebased = Adj_Close / base) |>
  ungroup()

# Compute equal-weight average index
movie_index <- media_rebased |>
  group_by(Date) |>
  summarize(
    Movie_Index = mean(rebased, na.rm = TRUE)
  )

sectors_rebased <- sectors |>
  group_by(Ticker, Sector) |>
  arrange(Date, .by_group = TRUE) |>
  mutate(
    base = first(`Adj Close`),
    rebased = `Adj Close` / base
  ) |>
  ungroup()

# Sector ETF index
sector_index <- sectors_rebased |>
  select(Date, Sector, rebased)

# Movie Index needs a pseudo "Sector" label
movie_index2 <- movie_index |>
  mutate(Sector = "Movie Industry")

combined <- bind_rows(
  sector_index,
  movie_index2 |> mutate(rebased = Movie_Index)
)
```

```{r}
combined2 <- combined  

ggplot() +
  # 1. All other sectors: normal colors, thinner, slightly transparent
  geom_line(
    data = combined2 |> filter(Sector != "Movie Industry"),
    aes(x = Date, y = rebased, colour = Sector),
    linewidth = 0.6,
    alpha = 0.6
  ) +
  # 2. Movie industry: bold red, thicker
  geom_line(
    data = combined2 |> filter(Sector == "Movie Industry"),
    aes(x = Date, y = rebased, colour = Sector),
    linewidth = 1.6
  ) +
  scale_color_manual(
    values = c(
      "Consumer Staples" = "#bc80bd",
      "Energy"           = "#ff7f00",
      "Financials"       = "#1f78b4",
      "Health Care"      = "#33a02c",
      "Industrials"      = "#6a3d9a",
      "Movie Industry"   = "#d73027",   # bold red highlight
      "S&P 500"          = "black",
      "Technology"       = "#ffd92f"
    ),
    name = "Sector / Industry"
  ) +
  scale_y_log10(
    breaks = c(0.5, 1, 2, 3, 5),
    labels = c("0.5x", "1x", "2x", "3x", "5x")
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y"
  ) +
  labs(
    title = "Movie Industry vs Major Sector ETFs (Rebased to 1)",
    subtitle = "Movie industry index highlighted against major sector ETFs (log scale)",
    x = "Date",
    y = "Rebased price (log scale)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background  = element_rect(fill = "white", color = NA),
    panel.grid.minor = element_blank(),
    legend.position = "right"
  )

```

In this chart, the movie industry index is just the simple average of each company’s stock price after rebasing them to 1 on the start date. From 2019 to 2025, technology stocks rise the most overall, while energy fluctuates the most. The movie industry does well during the late-2020 to 2022 period, but after 2022 it falls behind most other sectors, which suggests its recovery is weaker and less steady than the broader market.

### Chart 5. Stock Price Performance of Movie Companies From 2019–2025

```{r}
media_rebased <- media |>
  group_by(Ticker) |>
  arrange(Date, .by_group = TRUE) |>
  mutate(
    base    = first(Adj_Close),
    rebased = Adj_Close / base,
    ret     = log(rebased / dplyr::lag(rebased))  # daily log return
  ) |>
  ungroup()

vol_df <- media_rebased |>
  group_by(Ticker) |>
  summarize(
    vol = sd(ret, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(vol))

# Choose top 3 most volatile tickers
highlight_tickers <- vol_df$Ticker[1:3]
```

```{r}
# 1. Which tickers do we want to highlight?
highlight_tickers    <- highlight_tickers          
highlight_all        <- c(highlight_tickers, "^GSPC")

# Optional: nicer label for S&P
media_rebased <- media_rebased |>
  mutate(Ticker_label = if_else(Ticker == "^GSPC", "S&P 500", Ticker))

ggplot() +
  # --- Background: all other tickers in grey ---
  geom_line(
    data = media_rebased |> filter(!Ticker %in% highlight_all),
    aes(x = Date, y = rebased, group = Ticker),
    color = "grey80",
    linewidth = 0.5,
    alpha = 0.7
  ) +
  # --- Highlight: top 3 most volatile tickers ---
  geom_line(
    data = media_rebased |> filter(Ticker %in% highlight_tickers),
    aes(x = Date, y = rebased, color = Ticker_label),
    linewidth = 1.4
  ) +
  # --- Highlight: S&P 500 (black line) ---
  geom_line(
    data = media_rebased |> filter(Ticker == "^GSPC"),
    aes(x = Date, y = rebased, color = Ticker_label),
    linewidth = 1.4
  ) +
  # manual colors: black for S&P, Dark2 for the 3 volatile names
  scale_color_manual(
    name   = "Highlighted tickers",
    values = c(
      "S&P 500" = "black",
      RColorBrewer::brewer.pal(length(highlight_tickers), "Dark2") |>
        setNames(highlight_tickers)
    )
  ) +
  scale_y_log10(
    breaks = c(0.1, 0.2, 0.5, 1, 2, 5, 10),
    labels = c("0.1x", "0.2x", "0.5x", "1x", "2x", "5x", "10x")
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y"
  ) +
  labs(
    title = "Stock Price Performance of Movie Companies From 2019–2025",
    subtitle = "Top 3 most volatile tickers and the S&P 500 highlighted; prices rebased to 1 at first date",
    x = "Date",
    y = "Rebased price (log scale)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background  = element_rect(fill = "white", color = NA),
    panel.grid.minor = element_blank()
  )


```

This chart shows that two companies drove much of the volatility in the movie industry, helping explain the sector’s brief strength from late 2020 to 2022 (see chart 4). For example, Roku’s share price rose sharply in 2020, corresponding to higher streaming usage during stay-at-home conditions. AMC experienced large price swings in early 2021. This was due to the “meme-stock” trading frenzy driven by movements from the reddit group wallstreetbets. These movements stood out from the rest of the movie industry. However, in 2022, both ROKU and AMC collapsed, and this reveals these were temporary movements rather than lasting increase.

### Chart 6. Sector Cumulative Performance Since 2019

```{r}
# 1) Get final rebased level for each Sector
final_perf <- combined |>
  arrange(Sector, Date) |>
  group_by(Sector) |>
  filter(!is.na(rebased)) |>
  slice_tail(n = 1) |>
  ungroup() |>
  transmute(
    Sector,
    multiple = rebased              
  ) |>
  mutate(
    Sector  = forcats::fct_reorder(Sector, multiple),
    is_movie = (Sector == "Movie Industry"),
    label   = paste0("×", round(multiple, 1))
  )

ggplot(final_perf, aes(x = Sector, y = multiple, fill = is_movie)) +
  geom_col() +
  geom_text(
    aes(label = label),
    hjust = -0.15,
    size = 3.2
  ) +
  coord_flip(clip = "off") +
  scale_fill_manual(
    values = c("FALSE" = "grey70", "TRUE" = "#d73027"),
    guide  = "none"
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.15)),
    breaks = pretty(final_perf$multiple),
    labels = function(x) paste0("×", round(x, 1))
  ) +
  labs(
    title    = "Sector Cumulative Performance Since 2019",
    subtitle = "Each bar shows final rebased level (2019 = 1)",
    x = NULL,
    y = "Rebased level (× starting value)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.major.y = element_blank(),
    plot.margin        = margin(5.5, 40, 5.5, 5.5)
  )
```

This chart shows how much each sector has grown/recovered relative to its 2019 level. Technology has nearly quintupled, most sectors, including the S&P 500 as baseline, have roughly doubled or a bit more, but the movie industry is only about 1.7× its starting value, which again confirms its slow recovery.

## 3. Performance of sub-industries within the movie industry differ

From previous two sections, we’ve seen the movie industry indeed is smaller than before COVID and recovers much slower than other industries, and that this is not just a general market trend. To dig deeper, we now look inside the industry, since different types of companies, such as streamers, theater, studios, and diversified media firms, may not move in the same way. So, tn this section, we break the movie industry into these sub-industries to explore what actually happens.

### Chart 7. Faceted Sub-Industry in Movie Industry Performance

```{r}
# 1. Rebase each ticker
media_rebased <- media |>
  filter(!is.na(Adj_Close)) |>
  group_by(Ticker, SubIndustry) |>
  arrange(Date, .by_group = TRUE) |>
  mutate(
    base    = first(Adj_Close),
    rebased = Adj_Close / base
  ) |>
  ungroup()

# 2. Equal-weighted average within each sub-industry by date
sub_avg <- media_rebased |>
  group_by(SubIndustry, Date) |>
  summarize(
    rebased_avg = mean(rebased, na.rm = TRUE),
    .groups = "drop"
  )

# 3. Compute volatility of each sub-industry (based on log returns)
sub_vol <- sub_avg |>
  group_by(SubIndustry) |>
  arrange(Date, .by_group = TRUE) |>
  mutate(ret = log(rebased_avg / lag(rebased_avg))) |>
  summarize(
    vol = sd(ret, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(vol))

# 4. Order facets from most to least volatile
sub_avg <- sub_avg |>
  mutate(SubIndustry = factor(SubIndustry, levels = sub_vol$SubIndustry))

# 5. Plot: one average line per sub-industry, faceted
ggplot(sub_avg, aes(Date, rebased_avg)) +
  geom_line(color = "#2c7fb8", linewidth = 1) +
  facet_wrap(~ SubIndustry, ncol = 2) +
  scale_y_log10(
    breaks = c(0.25, 0.5, 1, 2, 4, 8),
    labels = c("0.25x", "0.5x", "1x", "2x", "4x", "8x")
  ) +
  scale_x_date( 
    date_breaks = "1 year", date_labels = "%Y" 
  ) +
  labs(
    title = "Faceted Sub-Industry in Movie Industry Performance",
    subtitle = "Equal-weighted average rebased stock prices, ordered by volatility (log scale)",
    y = "Average rebased price (log scale)",
    x = "Date"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background  = element_rect(fill = "white", color = NA),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "grey90"),
    strip.text = element_text(size = 14, face = "bold"),
    panel.spacing = grid::unit(1.2, "lines"),
    plot.title.position = "plot",
    axis.text.x = element_text(size = 9)
  )


```

Theater companies and streamer companies exhibit the most volatility. Theater companies experienced a steep drop in stock price in 2020 followed by an uneven recovery. Streamers rise sharply through 2020–2021 before dropping significantly in 2022. Diversified media firms trend more steadily upward, while studios show a mild, gradual decline.

### Chart 8. Correlation Between Movie Sub-Industries (2015–2025)

```{r}
# --- Rebase, build subindustry index, make wide matrix ---
media_rebased <- media |>
  filter(!is.na(Adj_Close)) |>
  group_by(Ticker) |>
  arrange(Date, .by_group = TRUE) |>
  mutate(
    base    = first(Adj_Close),
    rebased = Adj_Close / base
  ) |>
  ungroup()

subindustry_index <- media_rebased |>
  group_by(Date, SubIndustry) |>
  summarize(SubIndex = mean(rebased, na.rm = TRUE), .groups = "drop")

order_vec <- c("Benchmark", "Streamer", "Diversified", "Studio", "Theater")

sub_wide <- subindustry_index |>
  pivot_wider(names_from = SubIndustry, values_from = SubIndex) |>
  select(all_of(order_vec))

cor_mat <- cor(sub_wide, use = "pairwise.complete.obs")

cor_long <- cor_mat |>
  as.data.frame() |>
  rownames_to_column("Var1") |>
  pivot_longer(cols = all_of(order_vec),
               names_to = "Var2",
               values_to = "Correlation") |>
  mutate(
    Var1 = factor(Var1, levels = order_vec),
    Var2 = factor(Var2, levels = order_vec)
  )

# --- Plot heatmap with better color scale ---
ggplot(cor_long, aes(Var1, Var2, fill = Correlation)) +
  geom_tile(color = "white", linewidth = 0.4) +
  geom_text(aes(label = round(Correlation, 2)), size = 3) +
  scale_fill_gradient2(
    low  = "#2166ac",   # blue for negative correlations
    mid  = "white",     # zero
    high = "#b2182b",   # red for positive correlations
    midpoint = 0,
    limits = c(min(cor_long$Correlation), 1),
    name = "Correlation"
  ) +
  coord_fixed() +
  labs(
    title = "Correlation Between Movie Sub-Industries (2015–2025)",
    subtitle = "Diverging color scale centered at zero highlights negative vs. positive relationships",
    x = NULL, y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank(),
    plot.title.position = "plot"
  )


```

Diversified media firms move most closely with the overall market (correlation 0.84). Studios and theaters are moderately linked (0.66), and streamers and studios also track each other pretty well (0.74). Theaters are the real outlier here, as their prices move much less in sync with the rest of the industry. This suggests that theater companies, especially AMC, react to a different set of forces than streaming or diversified media firms.

### Chart 9. Density of Daily Returns by Sub-Industry (2019- 2025)

```{r}
# 1. Subindustry daily returns
sub_daily <- media |>
  filter(!is.na(return)) |>
  group_by(Date, SubIndustry) |>
  summarize(sub_ret = mean(return, na.rm = TRUE), .groups = "drop")

# 2. Order subindustries by volatility 
sub_order <- sub_daily |>
  group_by(SubIndustry) |>
  summarize(sd_ret = sd(sub_ret, na.rm = TRUE), .groups = "drop") |>
  arrange(desc(sd_ret)) |>
  pull(SubIndustry)

sub_daily <- sub_daily |>
  mutate(SubIndustry = factor(SubIndustry, levels = sub_order))

# 3. Ridgeline plot with less overlap
ggplot(sub_daily, aes(x = sub_ret, y = SubIndustry, fill = SubIndustry)) +
  geom_density_ridges(alpha = 0.8, scale = 1.2) + 
  scale_x_continuous(
    labels = percent,
    limits = c(-0.08, 0.08)
  ) +
  labs(
    title = "Density of Daily Returns by Sub-Industry (2019- 2025)",
    subtitle = "Zoomed in on typical daily moves (±8%)",
    x = "Daily return",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    panel.background = element_rect(fill = "white", color = NA)
  )

```

This chart shows on day-to-day moves. Benchmark and diversified firms have the tightest, tallest curves, so their daily returns usually stay close to zero. Studio stocks sit in the middle. Streamers have fatter tails, meaning they have bigger fluctuations more often. And again, theater stocks are the most volatile of all, with the widest distribution and most frequent large positive and negative returns

### Chart 10. How Movie/Media Stocks Move Across Performance Buckets Over Time

```{r}
# 1) Add regime labels -----------------------------------------------------
media_regime <- media |>
  mutate(
    Date = as.Date(Date),
    regime = case_when(
      Date < as.Date("2020-02-20") ~ "Pre-COVID",
      Date >= as.Date("2020-02-20") & Date <= as.Date("2021-12-31") ~ "COVID & stimulus",
      Date >= as.Date("2022-01-01") & Date <= as.Date("2022-12-31") ~ "Rate hikes / inflation",
      Date >= as.Date("2023-01-01") ~ "AI / recent",
      TRUE ~ NA_character_
    )
  ) |>
  filter(!is.na(regime), !is.na(return))

# 2) Cumulative return per Ticker × SubIndustry × Regime ------------------
regime_perf <- media_regime |>
  group_by(Ticker, SubIndustry, regime) |>
  summarize(
    cum_ret = prod(1 + return, na.rm = TRUE) - 1,
    .groups = "drop"
  )

# 3) Bucket each ticker into Low / Mid / High within each regime ----------
regime_buckets <- regime_perf |>
  group_by(regime) |>
  mutate(
    q1 = quantile(cum_ret, 0.33, na.rm = TRUE),
    q2 = quantile(cum_ret, 0.67, na.rm = TRUE),
    bucket = case_when(
      cum_ret <= q1 ~ "Low",
      cum_ret >= q2 ~ "High",
      TRUE          ~ "Mid"
    )
  ) |>
  ungroup() |>
  mutate(
    bucket = factor(bucket, levels = c("High", "Mid", "Low"))  # High at top
  )

# 4) Order regimes for the x-axis -----------------------------------------
regime_levels <- c("Pre-COVID", "COVID & stimulus",
                   "Rate hikes / inflation", "AI / recent")

# labels with date ranges on a second line
regime_labels <- c(
  "Pre-COVID"            = "Pre-COVID\n(< Feb, 2020)",
  "COVID & stimulus"     = "COVID & stimulus\n(Feb, 2020–Dec, 2021)",
  "Rate hikes / inflation" = "Rate hikes / inflation\n(2022)",
  "AI / recent"          = "AI / recent\n(2023–2025)"
)

flow_df <- regime_buckets |>
  filter(regime %in% regime_levels) |>
  filter(!is.na(SubIndustry), SubIndustry != "NA") |>
  mutate(
    regime      = factor(regime, levels = regime_levels),
    SubIndustry = fct_drop(SubIndustry)   # <-- drop unused "NA" level
  )

ggplot(
  flow_df,
  aes(x = regime,
      stratum = bucket,
      alluvium = Ticker,
      y = 1,
      fill = SubIndustry)
) +
  geom_flow(
    stat = "alluvium",
    lode.guidance = "forward",
    color = "grey70",
    alpha = 0.4
  ) +
  geom_stratum(fill = "grey90", color = "black") +
  geom_text(
    stat = "stratum",
    aes(label = after_stat(stratum)),
    size = 3,
    color = "black"
  ) +
  scale_x_discrete(labels = regime_labels) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "How Movie/Media Stocks Move Across Performance Buckets Over Time",
    subtitle = "Each stream is a ticker; buckets based on cumulative return in each regime",
    x = "Regime",
    y = "Number of tickers",
    fill = "Subindustry"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid       = element_blank(),
    plot.title       = element_text(margin = margin(b = 6)),
    plot.subtitle    = element_text(margin = margin(b = 10)),
    plot.title.position = "plot",
    axis.text.x      = element_text(lineheight = 0.9)
  )
```
Because there are only a handful of companies in each sub-industry, this alluvial chart is more noisy and the patterns are less obvious. The flows should be read as illustrative of broad shifts rather than precise estimates of how every part of the industry moved.

```{r}
regime_order <- c("Pre-COVID",
                  "COVID & stimulus",
                  "Rate hikes / inflation",
                  "AI / recent")

regime_sub <- media_regime |>
  group_by(SubIndustry, regime) |>
  summarize(
    cum_ret = prod(1 + return, na.rm = TRUE) - 1,
    .groups = "drop"
  ) |>
  mutate(
    regime = factor(regime, levels = regime_order)
  )

ggplot(regime_sub,
       aes(x = regime, y = cum_ret, fill = SubIndustry)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent) +
  labs(
    title = "Cumulative Return by Subindustry and Regime",
    subtitle = "COVID & stimulus period supercharged streamers; theaters lag in later regimes",
    x = "",
    y = "Cumulative return in regime"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

```{r}
# 1) Movie industry equal-weight price index (use Adj_Close, not rebased)
movie_index <- media |>
  filter(SubIndustry != "Benchmark") |>
  group_by(Date) |>
  summarize(
    movie_price = mean(Adj_Close, na.rm = TRUE),
    .groups = "drop"
  )

# 2) S&P 500
sp <- media |>
  filter(Ticker == "^GSPC") |>
  select(Date, sp_price = Adj_Close)

# 3) Netflix
nflx <- media |>
  filter(Ticker == "NFLX") |>
  select(Date, nflx_price = Adj_Close)

# 4) Align dates and rebase all three to 1 at common start
all3 <- movie_index |>
  inner_join(sp, by = "Date") |>
  inner_join(nflx, by = "Date") |>
  arrange(Date)

base_movie <- first(all3$movie_price)
base_sp    <- first(all3$sp_price)
base_nflx  <- first(all3$nflx_price)

relative_long <- all3 |>
  mutate(
    `Movie Industry` = movie_price / base_movie,
    `S&P 500`        = sp_price    / base_sp,
    `Netflix`        = nflx_price  / base_nflx
  ) |>
  select(Date, `Movie Industry`, `S&P 500`, `Netflix`) |>
  pivot_longer(
    cols = -Date,
    names_to = "Series",
    values_to = "rebased"
  )

ggplot(relative_long, aes(Date, rebased, color = Series)) +
  geom_line(linewidth = 1) +
  scale_y_log10() +
  labs(
    title = "Netflix vs Movie Industry vs S&P 500 (Rebased)",
    subtitle = "Netflix tracks the broad market more closely than the struggling movie industry",
    x = "Date",
    y = "Rebased Price (log scale)",
    color = ""
  ) +
  theme_minimal()
```
